\stepcounter{tableCounter} % Increment counter
\setcounter{rowCounter}{0} % Reset counter
\begin{tabularx}{\textwidth}{|>{\columncolor{tableColumnColor}}c|>{\columncolor{tableColumnColor}}c|>{\hsize=1.2\hsize}X|>{\hsize=.8\hsize}X|}
  \hline
  \rowcolor{tableHeaderColor}
  ID & Check & Description & Comments \\ \hline
    \procedureItem{Collect all necessary engine parts:
  \begin{itemize}
    \item 1x Mark I injector manifold  
    \item 1x Mark I pintle injector  
    \item 2x Mark I engine cap clamps 
    \item 4x M5 8.8 10mm screws
    \item 2x Static pressure sensors (Trafag)
    \item 2x Copper gaskets 
    \item G3/8 plug (igniter port)
    \item Thermocouple with G1/4 fitting 
    \item Sealing HITEC® O-Ring FKM 75.16-04 ID 27,00 x 1,50 mm 
  \end{itemize}
  
    Tools:
  \begin{itemize}
    \item 1x Torque wrench
    \item 2x Adjustable wrenches 
    \item Socket wrench set 
  \end{itemize}

    Material:
  \begin{itemize}
    \item Acetone
    \item Isopropanol
    \item Distilled water
    \item Nitril Gloves
    \item Paper towel
    \item Plastic Foil
    \item Heat conducting paste  
  \end{itemize}}{}
  \procedureItem{Clean pintle injector as per \underline{CFOS}.}{}
  \procedureItem{Place HITEC sealing in pintle injector sealing grove of the injector manifold. Ensure not to scratch the top or bottom sealing surfaces of the injector manifold.}{}
  \procedureItem{Mount pintle injector onto injector manifold.}{}
  \procedureItem{Apply heat conducting paste to the thermocouple with G1/4 fitting.}{}
  \procedureItem{Mount themrmocouple with G1/4 fitting onto injector manifold.}{}
  \procedureItem{Mount both static pressure sensors with a copper gasket. Ensure the copper gasket is centered properly (this ensures a leak-tight seal).}{}
  \procedureItem{Mount G3/8 plug onto igniter port of injector manifold.}{}
  
\end{tabularx}
