\stepcounter{tableCounter} % Increment counter
\setcounter{rowCounter}{0} % Reset counter
\begin{tabularx}{\textwidth}{|>{\columncolor{tableColumnColor}}c|>{\columncolor{tableColumnColor}}c|>{\hsize=1.2\hsize}X|>{\hsize=.8\hsize}X|}
  \hline
  \rowcolor{tableHeaderColor}
  ID & Check & Description & Comments \\ \hline
  
  \cellcolor{cyan}
  \procedureItem{Write down starting time}{Start Time:}
  
  \cellcolor{cyan}
  \procedureItem{If not already done: Hand out Hi-Vis jackets:
    \begin{itemize}
      \item TC: blue
      \item SO: green
      \item EIC: orange
      \item DACS: yellow
      \item LGO: yellow
      \item Visitors: yellow
      \item Supervisors: yellow
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{Gather everyone in front of the HANGAR and perform an attendance check (sec. B)}{}
  
  \cellcolor{cyan}
  \procedureItem{Inform about the role assignment (sec. B)}{}
  
  \cellcolor{cyan}
  \procedureItem{Read out behaviour rules:
    \begin{itemize}
      \iftoggle{firing}{\item Between briefing and debriefing, all present people are to wear warning vests and Visitor Badges (military)}{}
      \item Inform TC and SO when task is completed
      \item If you have no current task, wait in the \iftoggle{firing}{HUT}{Mission Control} and do not disturb other working members
      \item No one is to leave the area visible from the \iftoggle{firing}{HUT}{Mission Control} (as soon as we are there)
      \item If you need to go to the toilet, do it right after the briefing
      \item When going to the toilet, let other people know
      \iftoggle{firing}{\item You are NOT allowed to take any pictures or videos inside the HUT}{}
      \item The test consists of \iftoggle{firing}{12}{11} phases: Pre-Preparation (already over), Briefing (right now), Preparation \& Assembly, Transfer to Testing Area, Installation and Pre-\iftoggle{firing}{Firing}{Coldflow} Checks, Filling\iftoggle{firing}{\& Ignition Test}{}, \iftoggle{firing}{Firing}{Coldflow}, Safe State Establishment, Post-\iftoggle{firing}{Firing}{Coldflow} Checks \& Deinstallation, Return to Hangar, Disassembly \& Inspection, and we end with a Debriefing
      \item Radio communication: Always use call signs ("TC to DACS") and wait for confirmation ("come in") before message.
      \item Read out the test description (sec. A) (goals of the test)
      \item Go through the test parameters (sec. C)
    \end{itemize}
    Questions? Remarks?
  }{}
  
  \cellcolor{green}
  \procedureItem{Hand out safety goggles (Can also be done at the test site, note: for handling N$_2$ bottle, safety goggles are mandatory)}{}
  
  \cellcolor{green}
  \procedureItem{If cryogenic liquids are involved in the test: Check that all people who will be working on the system wear proper clothing:
    \begin{itemize}
      \item Prevent electrostatic charging 
      \item Avoid porous textiles that can be saturated with liquids
      \item Ideally, thin cotton textiles (covered by a non-porous second skin, like a raincoat)
      \item EIC has to wear adequate footwear.
    \end{itemize}
  }{}
  
  \cellcolor{green}
  \procedureItem{Inform about safety points:
    \begin{itemize}
      \item Focus
      \item Follow the procedure so that nothing is forgotten (even if you know the steps by heart)
      \item Work efficiently but do not rush
      \item If something does not go as planned or seems suspicious, inform the TC and SO
      \item If you notice unauthorized people, animals, cars, airplanes near the testing location, inform the TC and SO
      \item Wear safety equipment as specified in the procedures
      \item Between briefing and debriefing, all present people inside the safety zone are to wear eye and ear protection
      \item In case of an incident: First, keep calm and think. Do not endanger yourself. Then react. Use the contingency procedures. Emergency responsibilities are defined
      \item Show the location of Contingency Procedures and how to use them (for new visitors only)
      \item Confirm that everyone has read the Operation Safety Concept
      \item Confirm that everyone has filled out the Emergency Contact List
      \item Check if anyone has allergies, if yes check that they have proper medication on them.
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{$\rightarrow$ TC announces start of the \textbf{Test}}{}
  
  \cellcolor{cyan}
  \procedureItem{If \textbf{Preparation \& Assembly} is next Phase:

    $\rightarrow$ go to step 3.1.
  }{}
  
  \cellcolor{cyan}
  \procedureItem{If \textbf{Transfer to Testing Area} is next Phase:

    $\rightarrow$ go to step 4.1.
  }{}
  
\end{tabularx}