\stepcounter{tableCounter} % Increment counter
\setcounter{rowCounter}{0} % Reset counter
\begin{tabularx}{\textwidth}{|>{\columncolor{tableColumnColor}}c|>{\columncolor{tableColumnColor}}c|>{\hsize=1.2\hsize}X|>{\hsize=.8\hsize}X|}
  \hline
  \rowcolor{tableHeaderColor}
  ID & Check & Description & Comments \\ \hline
  
  \cellcolor{cyan}
  \procedureItem{Write down starting time}{Start Time: }
  
  \cellcolor{cyan}
  \procedureItem{If not immediately after briefing:
    \begin{itemize}
      \item Gather everyone in front of the HANGAR and perform an attendance check (sec. B)
      \item TC informs about upcoming \textbf{Transfer to Airfield}
    \end{itemize}
  }{}
  
\iftoggle{firing}{  \cellcolor{green}
  \procedureItem{If not already done: Hand out access badges}{}}{}
  
  \cellcolor{green}
  \procedureItem{Ensure everyone wears proper Hi-Vis jacket}{}
  
\iftoggle{firing}{  \cellcolor{green}
  \procedureItem{Ensure everyone wears access badge clearly visible}{}}{}
  
  \cellcolor{cyan}
  \procedureItem{Hand out the following procedures:
    \begin{itemize}
      \item \textit{\textbf{Installation Trailer}}
      \item \textit{\textbf{Installation DACS}}
      \item \textit{\textbf{KiDAQ}} (if necessary)
      \item \textit{\textbf{Installation PSS}}
      \iftoggle{firing}{\item \textit{\textbf{Installation Igniter}}}{}
    \end{itemize}
  }{}
  
\multicolumn{4}{|c|}{\cellcolor{tableColumnColor} \textbf{Transfer to Test Area}} \\ \hline
  \iftoggle{firing}{\cellcolor{cyan}
  \procedureItem{Route:
    \begin{itemize}
      \item Through main gate
      \item Emergency Car (Driver \& SO) goes first
      \item Open the gate and wait until all attendees are passed through, close the gate again and put the key for the main gate on the driver’s seat of the Emergency Car (as soon as it’s parked)
      \item \textbf{DO NOT LEAVE THE GATE OPEN AT ANY TIME!!}
    \end{itemize}
  }{}}{}
  % Write new
  
\multicolumn{4}{|c|}{\cellcolor{tableColumnColor} \textit{Behaviour: }} \\ \hline

\cellcolor{cyan}
  \procedureItem{If it is raining:
    \begin{itemize}
      \item Make sure to load tent/pavilion into Towing Car Trailer
      \item Install tent/pavilion before unloading all material
      \item Secure tent/pavilion in place with weights
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{Driver Emergency Car:
    \begin{itemize}
      \item Unload GEN/SFTY/DACS/Snacks \& Beverages/Cable Roll at HUT
      \item Unload all other material at trailer
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{Safety Officer:
    \begin{itemize}
      \item Open HUT and leave key on the inside lock of the door
      \item Tape \textit{\underline{Warning Sign}} onto two empty boxes and position them on both sides of the safety zone (roughly 100m from the trailer). If aluminum profiles are available, use aluminum profiles.
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{Driver Towing Car Trailer:
    \begin{itemize}
      \item Place the trailer at the testing location as shown in the \underline{\textit{Operation Safety Concept}} (between \textbf{Marking 46 and 47}, closer to 46)
      \item Unload all material from the Towing Car. \textbf{Leave the N$_2$ Bottles in the car until they can be fixed to the structures!}
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{Other:
    \begin{itemize}
      \item Place the LOX Dewar at the border of the safety zone as shown in the \underline{\textit{Operation Safety Concept}} and ensure that it is secured properly (wear safety goggles and cryo-gloves during the entire transport). The Dewar can either be pulled at the handle or pushed.
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{As soon as done with transfer:
    \begin{itemize}
      \item SO: Install the safety equipment according to \underline{\textit{Operation Safety Concept}}
      \item ENG: Install the Trailer according to \underline{\textit{Installation Trailer}}, install Water Pump
      \item DACS: Install the control station according to \textit{\underline{Installation Control}}, install hardware according to \textit{\underline{Installation Hardware Check}}, install surveillance cameras according to \textit{\underline{Installation Surveillance}}, install KiDAQ according to \textit{\underline{KiDAQ}}
    \end{itemize}
  }{Installing the water pump includes filling the water container with water. If the grass behind the trailer is dry, the water pump can be used to water the grass. Don't forget to bleed the water pump, it shall not suck air into the system!}
  
  \cellcolor{cyan}
  \procedureItem{As soon as trailer is installed:
    \begin{itemize}
      \item ENG: Install igniter according to \textit{\underline{Installation Igniter}}
      \item PSS: Install PSS according to \textit{\underline{Installation PSS}}
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{Questions? Remarks?
    \begin{itemize}
      \item $\rightarrow$ End of briefing
    \end{itemize}
  }{}
  
  \cellcolor{cyan}
  \procedureItem{$\rightarrow$ Transfer to Airfield}{}
  
  \cellcolor{cyan}
  \procedureItem{Collect completed and signed \textit{\underline{Installation Trailer from ENG1}}}{}
  
  \cellcolor{cyan}
  \procedureItem{Collect completed and signed \textit{\underline{Installation DACS}} from DACS1}{}
  
  \cellcolor{cyan}
  \procedureItem{Collect completed and signed \textit{\underline{Installation PSS}} from PSS1}{}
  \iftoggle{firing}{
  \cellcolor{cyan}
  \procedureItem{Collect completed and signed \textit{\underline{Installation Igniter}} from ENG1}{}
  }{}
  \cellcolor{cyan}
  \procedureItem{$\leftrightarrow$ TC to all: Installation is completed}{}

\end{tabularx}