
\begin{tabularx}{0.9\textwidth}{|>{\columncolor{tableColumnColor}}c|c|X|}
    \hline
    \rowcolor{tableHeaderColor}
    Check & Amount & Description \\ \hline

    \multicolumn{3}{|>{\columncolor{tableColumnColor}}c|}{\textbf{PSS Rolling Table}} \\ \hline

    \checklistItem{2x}{Span Set}
    
    \checklistItem{1x}{
      \begin{minipage}[t]{\linewidth}
        Pressure Reducer PRG (if not installed on trailer)
      \end{minipage}  
      }

      \checklistItem{5x}{PTFE Sealings for Bottle Connections}

    \checklistItem{5x}{Copper Gaskets for Pressure Sensors}

    \checklistItem{1x}{Box with Festo Pipe \& Connectors}
    
    \checklistItem{1x}{Box with Insulation}

    \checklistItem{1x}{Plastic Foil}

    \checklistItem{2 packs}{Nitril Gloves}

    \checklistItem{1x}{Cord}

    \checklistItem{1 roll}{Masking Tape}

    \checklistItem{1 roll}{Duct Tape}

    \checklistItem{2 rolls}{Teflon Tape 1/2 in.}

    \checklistItem{2 rolls}{Teflon Tape 1/4 in.}

    \checklistItem{1x}{Zip ties}

    \checklistItem{1 roll}{Paper Towels}

    \checklistItem{1x}{Weights for the tents}

    \checklistItem{1 bottle}{Distilled Water}

    \checklistItem{1 bottle}{Acetone}

    \checklistItem{1 bottle}{Isopropanol}

    \checklistItem{2 bottles}{Snoop (check that they are sufficiently full)}

    \checklistItem{1x}{P-Reducer Wrnech (32mm)}

    \checklistItem{1x}{Adjustable Wrench}

    \checklistItem{1x}{Trash Box}

    \multicolumn{3}{|c|}{\textit{For FSS CF/Firing}} \\ \hline
    
    \checklistItem{1x}{Measuring Cup}
    
    \checklistItem{1x}{Funnel}
    
    \checklistItem{1x}{Fill Line}
    
    \checklistItem{1x}{Drain Container}

    \multicolumn{3}{|c|}{\textit{For OSS CF/Firing}} \\ \hline
    
    \checklistItem{1x}{Flexible pipe (Dewar)}

    \checklistItem{2x}{Cryo Aprons}

    \checklistItem{2x}{Cryo Gloves}

    \checklistItem{1x}{Cryo Face Shield}

    \checklistItem{1x}{Normal Face Shield}

    \multicolumn{3}{|>{\columncolor{tableColumnColor}}c|}{\textbf{PSS Toolbox}} \\ \hline

    \checklistItem{1x}{Pen/Marker}

    \checklistItem{1x}{Box Cutter}

    \checklistItem{1x}{Tape Measure}

    \checklistItem{1x}{Rubber Bands}

    \checklistItem{1x}{Gap Inspector 1/2 in.}

    \checklistItem{1x}{Gap Inspector 1/4 in.}

    \checklistItem{1x}{Tweezers}

    \checklistItem{1x}{Spare Sparkplug}

    \checklistItem{4x}{Cap 1/2 in. M}

    \checklistItem{4x}{Cap 1/2 in. F}

    \checklistItem{4x}{Cap 1/4 in. M}

    \checklistItem{4x}{Cap 1/4 in. F}

    \checklistItem{1x}{Slotted Screwdriver (small)}
    
    \checklistItem{1x}{Slotted Screwdriver (medium)}

    \checklistItem{1x}{Slotted Screwdriver (large)}

    \checklistItem{1x}{Phillips Screwdriver (small)}

    \checklistItem{1x}{Phillips Screwdriver (medium)}

    \checklistItem{1x}{Phillips Screwdriver (large)}

    \checklistItem{2x}{Adjustable Wrench (small)}

    \checklistItem{2x}{Adjustable Wrench (medium)}

    \checklistItem{2x}{Hex Key Set 3 mm - 6 mm}

    \checklistItem{1x}{Side Cutter}

    \checklistItem{1x}{Sealing Removal Tools}

    \checklistItem{1x}{Wrenches 6 mm - 20 mm}

    \checklistItem{1x}{Hammer}

    \checklistItem{1x}{Rubber Mallet}

    \checklistItem{1x}{Level}
    
  \end{tabularx}

% If no tools required, delete previous lines and uncomment next line
% \textit{none}
  